systemfit: A Package for Estimating\\ Systems of Simultaneous Equations in \proglang{R}

### 2007-06-06 paper/trunk/systemfit_restrictions.tex
substituted "\COV" (defined in jss.cls) for all "\Cov"; removed definition(s) of "\Cov"
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@710 591db2bd-e0a0-4d22-8c19-2192dbb7da31
substituted "\E [ . ]" (\E is defined in jss.cls) for all "E ( . )" and "E [ . ]"
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@711 591db2bd-e0a0-4d22-8c19-2192dbb7da31
a few minor improvements
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@712 591db2bd-e0a0-4d22-8c19-2192dbb7da31
The paper no longer treats Omega as known in sections 2.1 and 2.2; the fact that Sigma and Omega

To impose these restrictions, the $X$ matrix is
(post-)\hspace{0pt}multiplied by this $M$ matrix, so that
\begin{equation}
    X^* = X \cdot M .
\end{equation}
Then, $X^*$ is substituted for $X$ and a standard estimation as described
in the previous section is done
(equations~\ref{eq:ols}--\ref{eq:3slsEViews}).
This results in the linear independent parameter estimates $\widehat{\beta}^*$ and
their covariance matrix.
The original parameters can be obtained by equation (\ref{eq:T-restr})
and the covariance matrix of the original parameters
can be obtained by
\begin{equation}
   \Cov \left[ \widehat{\beta} \right]
   = M \cdot \Cov \left[ \widehat{\beta}^* \right] \cdot M' .
\end{equation}

@@

The OLS estimator restricted by $R \beta^0 = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{OLS} \\ \widehat{\lambda}
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      X' X & R' \\ 
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      X' y \\ q 
   \end{array} \right] ,
\end{equation}
where $\lambda$ is a vector of the Lagrangean multipliers of the restrictions.
If the whole system is treated as one single equation,
the covariance matrix of the estimated parameters is
\begin{equation}
   \Cov 
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{OLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = \sigma^2 
   \left[ \begin{array}{cc}
      X' X & R' \\ 
      R & 0
   \end{array} \right]^{-1} ,
\end{equation}
where $\sigma^2 = E \left( u_{it}^2 \right)$.
If the disturbance terms of the individual equations
are allowed to have different variances, 
the covariance matrix of the estimated parameters is
\begin{equation}
   \Cov 
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{OLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      X' \Omega^{-1} X & R' \\ 
      R & 0
   \end{array} \right]^{-1} ,
\end{equation}
where $\Omega = \Sigma \otimes I$,
$\sigma_{ij} = 0 \; \forall \; i \neq j$ and
$\sigma_{ii} = \sigma_i^2 = E \left( u_{it}^2 \right)$.

@@

The WLS estimator restricted by $R \beta^0 = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{WLS} \\ \widehat{\lambda}
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      X' \Omega^{-1} X & R' \\ 
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      X' \Omega^{-1} y \\ q 
   \end{array} \right] ,
\end{equation}
where $\Omega = \Sigma \otimes I$,
$\sigma_{ij} = 0 \; \forall \; i \neq j$ and
$\sigma_{ii} = \sigma_i^2 = E \left( u_{it}^2 \right)$.
The covariance matrix of the estimated parameters is
\begin{equation}
   \Cov 
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{WLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      X' \Omega^{-1} X & R' \\ 
      R & 0
   \end{array} \right]^{-1} .
\end{equation}

@@

The SUR estimator restricted by $R \beta^0 = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{SUR} \\ \widehat{\lambda}
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      X' \Omega^{-1} X & R' \\ 
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      X' \Omega^{-1} y \\ q 
   \end{array} \right] ,
\end{equation}
where $\Omega = \Sigma \otimes I$ and
$\sigma_{ij} = E \left( u_{it} u_{jt} \right)$.
The covariance matrix of the estimated parameters is
\begin{equation}
   \Cov 
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{SUR} \\ \widehat{\lambda}
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      X' \Omega^{-1} X & R' \\ 
      R & 0
   \end{array} \right]^{-1} .
\end{equation}

@@

The 2SLS estimator restricted by $R \beta^0 = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{2SLS} \\ \widehat{\lambda}
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      \widehat{X}' \widehat{X} & R' \\ 
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      \widehat{X}' y \\ q 
   \end{array} \right] .
   \label{eq:beta2SLSr}
\end{equation}
If the whole system is treated as one single equation,
the covariance matrix of the estimated parameters is
\begin{equation}
   \Cov 
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{2SLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = \sigma^2 
   \left[ \begin{array}{cc}
      \widehat{X}' \widehat{X} & R' \\ 
      R & 0
   \end{array} \right]^{-1} ,
\end{equation}
where $\sigma^2 = E \left( u_{it}^2 \right)$.
If the disturbance terms of the individual equations
are allowed to have different variances, 
the covariance matrix of the estimated parameters is
\begin{equation}
   \Cov 
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{2SLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      \widehat{X}' \Omega^{-1} \widehat{X} & R' \\ 
      R & 0
   \end{array} \right]^{-1} ,
\end{equation}
where $\Omega = \Sigma \otimes I$,
$\sigma_{ij} = 0 \; \forall \; i \neq j$ and
$\sigma_{ii} = \sigma_i^2 = E \left( u_{it}^2 \right)$.

@@

The W2SLS estimator restricted by $R \beta^0 = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{W2SLS} \\ \widehat{\lambda}
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      \widehat{X}' \Omega^{-1} \widehat{X} & R' \\ 
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      \widehat{X}' \Omega^{-1} y \\ q 
   \end{array} \right] ,
\end{equation}
where $\Omega = \Sigma \otimes I$,
$\sigma_{ij} = 0 \; \forall \; i \neq j$ and
$\sigma_{ii} = \sigma_i^2 = E \left( u_{it}^2 \right)$.
The covariance matrix of the estimated parameters is
\begin{equation}
   \Cov 
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{W2SLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      \widehat{X}' \Omega^{-1} \widehat{X} & R' \\ 
      R & 0
   \end{array} \right]^{-1} .
\end{equation}

@@

      \widehat{X}' \Omega^{-1} \widehat{X} & R' \\ 

@@

      \widehat{X}' \Omega^{-1} y \\ q 

@@

where $\Omega = \Sigma \otimes I$ and
$\sigma_{ij} = E \left( u_{it} u_{jt} \right)$.
The covariance matrix of this estimator is

@@

   \Cov 

@@

      \widehat{X}' \Omega^{-1} X & R' \\ 

@@

      X' H \left( H' \Omega H \right)^{-1} H' X & R' \\ 

@@

      X' H \left( H \Omega H \right)^{-1} H' y \\ q 

@@

      \widehat{X}' \Omega^{-1} H \left( H' H \right)^{-1} H' y \\ q 

@@

      \widehat{X}' \Omega^{-1} H \left( H' H \right)^{-1} H' \Omega
      H \left( H' H \right)^{-1} H' \Omega^{-1} \widehat{X} & 0' \\ 

@@

The econometrics software EViews calculates the restricted 3SLS estimator by

@@

      \widehat{X}' \Omega^{-1} \left( y - X \widehat{\beta}^0_{2SLS} \right)

@@

To calculate the covariance matrix
EViews uses the standard formula of the restricted 3SLS
estimator~(\ref{eq:cov3slsr}).

>>>>

To impose these restrictions, the $X$ matrix is
(post-)\hspace{0pt}multiplied by this $M$ matrix, so that
\begin{equation}
    X^* = X \cdot M .
\end{equation}
Then, $X^*$ is substituted for $X$ and a standard estimation as described
in the previous section is done
(equations~\ref{eq:ols}--\ref{eq:3slsEViews}).
This results in the linear independent parameter estimates $\widehat{\beta}^*$ and
their covariance matrix.
The original parameters can be obtained by equation (\ref{eq:T-restr})
and the estimated covariance matrix of the original parameters
can be obtained by
\begin{equation}
   \COVHat \left[ \widehat{\beta} \right]
   = M \cdot \COVHat \left[ \widehat{\beta}^* \right] \cdot M' .
\end{equation}

@@

The OLS estimator restricted by $R \beta^0 = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{OLS} \\ \widehat{\lambda}
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      X' X & R' \\ 
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      X' y \\ q 
   \end{array} \right] ,
\end{equation}
where $\lambda$ is a vector of the Lagrangean multipliers of the restrictions.
If the whole system is treated as one single equation,
an estimator of the covariance matrix of the estimated parameters is
\begin{equation}
   \COVHat
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{OLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = \sHat^2 
   \left[ \begin{array}{cc}
      X' X & R' \\ 
      R & 0
   \end{array} \right]^{-1} ,
\end{equation}
where $\sHat$ is the estimated variance of the disturbance terms.
If the disturbance terms of the individual equations
are allowed to have different variances, 
an estimator of the covariance matrix of the estimated parameters is
\begin{equation}
   \COVHat
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{OLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      X' \OHat^{-1} X & R' \\
      R & 0
   \end{array} \right]^{-1} ,
\end{equation}
where $\OHat = \SHat \otimes I$,
$\sHat_{ij} = 0 \; \forall \; i \neq j$ and
$\sHat_{ii} = \sHat_i^2$ is the estimated variance
of the disturbance term in the $i$th equation.

@@

The WLS estimator restricted by $R \beta^0 = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{WLS} \\ \widehat{\lambda}
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      X' \OHat^{-1} X & R' \\
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      X' \OHat^{-1} y \\ q
   \end{array} \right] ,
\end{equation}
where $\OHat = \SHat \otimes I$,
$\sHat_{ij} = 0 \; \forall \; i \neq j$ and
$\sHat_{ii} = \sHat_i^2$ is the estimated variance
of the disturbance term in the $i$th equation.
An estimator of the covariance matrix of the estimated parameters is
\begin{equation}
   \COVHat
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{WLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      X' \OHat^{-1} X & R' \\
      R & 0
   \end{array} \right]^{-1} .
\end{equation}

@@

The SUR estimator restricted by $R \beta^0 = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{SUR} \\ \widehat{\lambda}
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      X' \OHat^{-1} X & R' \\
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      X' \OHat^{-1} y \\ q
   \end{array} \right] ,
\end{equation}
where $\OHat = \SHat \otimes I$ and
$\SHat$ is the estimated covariance matrix of the disturbance terms.
An estimator of the covariance matrix of the estimated parameters is
\begin{equation}
   \COVHat
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{SUR} \\ \widehat{\lambda}
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      X' \OHat^{-1} X & R' \\
      R & 0
   \end{array} \right]^{-1} .
\end{equation}

@@

The 2SLS estimator restricted by $R \beta^0 = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{2SLS} \\ \widehat{\lambda}
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      \widehat{X}' \widehat{X} & R' \\ 
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      \widehat{X}' y \\ q 
   \end{array} \right] .
   \label{eq:beta2SLSr}
\end{equation}
If the whole system is treated as one single equation,
an estimator of the covariance matrix of the estimated parameters is
\begin{equation}
   \COVHat
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{2SLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = \sHat^2 
   \left[ \begin{array}{cc}
      \widehat{X}' \widehat{X} & R' \\ 
      R & 0
   \end{array} \right]^{-1} ,
\end{equation}
where $\sHat^2$ is the estimated variance of the disturbance terms.
If the disturbance terms of the individual equations
are allowed to have different variances, 
an estimator of the covariance matrix of the estimated parameters is
\begin{equation}
   \COVHat
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{2SLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      \widehat{X}' \OHat^{-1} \widehat{X} & R' \\
      R & 0
   \end{array} \right]^{-1} ,
\end{equation}
where $\OHat = \SHat \otimes I$,
$\sHat_{ij} = 0 \; \forall \; i \neq j$ and
$\sHat_{ii} = \sHat_i^2$ is the estimated variance
of the disturbance term in the $i$th equation.

@@

The W2SLS estimator restricted by $R \beta^0 = q$ can be obtained by
\begin{equation}
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{W2SLS} \\ \widehat{\lambda}
   \end{array} \right]
   =
   \left[ \begin{array}{cc}
      \widehat{X}' \OHat^{-1} \widehat{X} & R' \\
      R & 0
   \end{array} \right]^{-1}
   \cdot
   \left[ \begin{array}{c}
      \widehat{X}' \OHat^{-1} y \\ q
   \end{array} \right] ,
\end{equation}
where $\OHat = \SHat \otimes I$,
$\sHat_{ij} = 0 \; \forall \; i \neq j$ and
$\sHat_{ii} = \sHat_i^2$ is the estimated variance
of the disturbance term in the $i$th equation.
An estimator of the covariance matrix of the estimated parameters is
\begin{equation}
   \COVHat
   \left[ \begin{array}{c}
      \widehat{\beta}^0_{W2SLS} \\ \widehat{\lambda}
   \end{array} \right] 
   = 
   \left[ \begin{array}{cc}
      \widehat{X}' \OHat^{-1} \widehat{X} & R' \\
      R & 0
   \end{array} \right]^{-1} .
\end{equation}

@@

      \widehat{X}' \OHat^{-1} \widehat{X} & R' \\

@@

      \widehat{X}' \OHat^{-1} y \\ q

@@

where $\OHat = \SHat \otimes I$ and
$\SHat$ is the estimated covariance matrix of the disturbance terms.
An estimator of the covariance matrix of the estimated parameters is

@@

   \COVHat

@@

      \widehat{X}' \OHat^{-1} X & R' \\

@@

      X' H \left( H' \OHat H \right)^{-1} H' X & R' \\

@@

      X' H \left( H \OHat H \right)^{-1} H' y \\ q

@@

      \widehat{X}' \OHat^{-1} H \left( H' H \right)^{-1} H' y \\ q

@@

      \widehat{X}' \OHat^{-1} H \left( H' H \right)^{-1} H' \OHat
      H \left( H' H \right)^{-1} H' \OHat^{-1} \widehat{X} & 0' \\

@@

The econometrics software \proglang{EViews} calculates the restricted 3SLS estimator by

@@

      \widehat{X}' \OHat^{-1} \left( y - X \widehat{\beta}^0_{2SLS} \right)

@@

\proglang{EViews} uses the standard formula of the restricted 3SLS
estimator~(\ref{eq:cov3slsr}) to calculate an estimator
for the covariance matrix of the estimated parameters.
